% icstdoc.tex V1.12 6 May 2011

\documentclass[fonts]{icst}

\usepackage{moreverb}

\usepackage[breaklinks,colorlinks,bookmarksopen,bookmarksnumbered,linkcolor=ICSTblue,citecolor=blue,urlcolor=ICSTblue]{hyperref}
\def\UrlBreaks{\do\/\do-\do.}

\usepackage{breakurl}
\usepackage{doi}

\usepackage{subcaption}


\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\volumeyear{2019}

\journalname{XXXXXX}
\articletype{Research Article/Editorial}
\setcounter{page}{01}
 \def\volumeyear{XXXX}
 \def\volumenumber{XX}
  \def\issuemonth{XX-XX}
  \def\issuenumber{X}
  \def\articleid{XX}
  \def\copyrightholder{Andrew Meyer\textit{ et al.}, licensed to ICST}
  \copyrightnote{This is an open access article distributed under the terms of the Creative Commons Attribution license (\url{http://creativecommons.org/licenses/by/3.0/}), which permits unlimited use, distribution and reproduction in any medium so long as the original work is properly cited.}
  \def\articledoi{10.4108/XX.X.X.XX}
\received{XXXX}
  \accepted{XXXX}
  \published{XXXX}

\begin{document}

\runningheads{A. Meyer, S. Roy}{NIST Standards Compliance of Metadata-Based Deleted-File-Recovery (DFR) Tools}

\title{NIST Standards Compliance of Metadata-Based Deleted-File-Recovery (DFR) Tools}

\author{Andrew Meyer\affil{1}\fnoteref{1}, Sankardas Roy\affil{2}\fnoteref{2}}

\address{\affilnum{1}Bowling Green State University, Bowling Green, Ohio, USA\\
\affilnum{2}Bowling Green State University, Bowling Green, Ohio, USA}

\abstract{Digital forensics (DF) tools are used for post-mortem investigation of cyber-crimes. 
National Institute of Standards and Technology (NIST) 
has set standards for DF tools. Compliance with the standards by DF tools is critical to ensure 
integrity of the outcome of forensics analysis. 
In this paper, we consider standardization of one class of DF tools for Deleted File Recovery (DFR). 
Via extensive experiments we evaluate frequently-used DFR tools on NIST standards, and 
find that tools do not satisfy some of the standards.  
We compile a comparative analysis of these tools, which could help the user choose the right DFR tool. 
We hope our findings will trigger more research activities on compliance of standards from the researcher community as well as the practitioners.}

\keywords{Deleted File Recovery, Digital Forensics, Metadata, NIST, Standards, File System, FAT, NTFS}

%\tnotetext[1]{Please ensure that you use the most up to date
%class file, available from EAI at \url{http://doc.eai.eu/publications/transactions/latex/}
%}

\fnotetext[1]{Corresponding author.  Email: \email{apmeyer@bgsu.edu}}
\fnotetext[2]{Corresponding author.  Email: \email{sanroy@bgsu.edu}}

\maketitle

\input{intro.tex}
\input{rq.tex}
\input{background.tex}
\input{approach.tex}
\input{discussion.tex}
\input{conclusion.tex}

\ack A. Meyer's work has been partially supported by a grant from BGSU's Center for Undergraduate Research and Scholarship 
(CURS) in summer of 2019. S. Roy's work has been partially supported by a NIST grant (grant number: 70NANB17H321; Year 2017-19) that he has been awarded with as a Co-PI. 
Quinton Currier at BGSU assisted with the testing process.

\bibliographystyle{icstnum}
\bibliography{mybib}

\end{document}
