%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Review Volume (last updated on 20-4-2015)                            %%
%% Trim Size: 9in x 6in                                                 %%
%% Text Area: 7.35in (include runningheads) x 4.5in                     %%
%% Main Text: 10 on 13pt                                                %%
%% For support: Yolande Koh, <ykoh@wspc.com.sg>                         %%
%%              D. Rajesh Babu, <rajesh@wspc.com.sg>                    %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%\documentclass[wsdraft]{ws-rv9x6} % to draw border line around text area
\documentclass{ws-rv9x6}
%\usepackage{subfigure}   % required only when side-by-side / subfigures are used
\usepackage{subcaption}
\usepackage{ws-rv-thm}   % comment this line when `amsthm / theorem / ntheorem` package is used
\usepackage{ws-rv-van}   % numbered citation & references (default)
%\usepackage{ws-index}   % to produce multiple indexes
\makeindex
%\newindex{aindx}{adx}{and}{Author Index}       % author index
%\renewindex{default}{idx}{ind}{Subject Index}  % subject index

\newcommand{\morecite}{{\color{red}{[citation]}}}
\newcommand{\TODO}[1]{\textcolor{red}{#1}} % for temporary working notes
\newenvironment{paraphrase}{\color{blue}}{\color{black}} % for text from old paper that needs to be paraphrased
\newcommand{\commentOut}[1]{} 
 
\begin{document}

\chapter[Evaluating DFR tools per NIST guidelines]{Evaluating DFR tools per NIST guidelines:\\ Results and critique \label{ra_ch1}}

\author[A. Meyer and S. Roy]{Andrew Meyer and S. Roy\footnote{Author footnote.}}
%\index[aindx]{Author, F.} % or \aindx{Author, F.}
%\index[aindx]{Author, S.} % or \aindx{Author, S.}

\address{Computer Science Department, BGSU,\\
Bowling Green, Ohio, USA 43403, \\
apmeyer@bgsu.edu\footnote{Affiliation footnote.}}
 
\begin{abstract}
To carry out post-mortem investigation of cyber-crimes, 
professionals use various digital forensics (DF) tools. 
To aid in the standardization of DF tools, 
National Institute of Standards and Technology (NIST)’s 
CFTT (Computer Forensics Tool Testing) program 
has compiled a set of expectations for these tools’ behavior. 
DF tools meeting these expectations is critical for the 
integrity of forensic analysis. In this article, we focus 
on standardization of Deleted File Recovery (DFR) tools, 
which is a specific class of DF tools. We design a set of 
test images across widely-used file systems (FAT and NTFS). 
We run extensive experiments on these test images as well as 
the test images provided by CFTT to evaluate the DFR tools, 
and to our surprise we find that many DFR tools that are available 
in the market do not fully meet the CFTT expectations. 
We report a comparative evaluation of these tools per CFTT 
expectations, which could help the user choose the right tool. 
We also identify the factors which make a DFR tool fail, and 
reflect on the applicability of the CFTT expectations. 
We hope that our current report will trigger more research 
on standardization of DFR tools from the researcher community.
\end{abstract}

%\markboth{Even Page Header}{Odd Page Header} % Customized running heads

\body

%\tableofcontents

\input{intro.tex}
\input{background.tex}
\input{rq.tex}
\input{approach.tex}
\input{discussion.tex}
\input{conclusion.tex}

%\section*{Acknowledgments}
%Acknowledgments to funding bodies etc. may be placed in a separate
%section at the end of the text, before the Appendices. This should not
%be numbered so use \verb|\section*{Acknowledgements}|.


\bibliographystyle{ws-rv-van}
\bibliography{bibfile}

%\blankpage
%\printindex[aindx]                 % to print author index
%\printindex                        % to print subject index

\end{document} 
