% icstdoc.tex V1.12 6 May 2011

\documentclass[fonts]{icst}

\usepackage{moreverb}

\usepackage[breaklinks,colorlinks,bookmarksopen,bookmarksnumbered,linkcolor=ICSTblue,citecolor=blue,urlcolor=ICSTblue]{hyperref}
\def\UrlBreaks{\do\/\do-\do.}

\usepackage{breakurl}
\usepackage{doi}

\usepackage{subcaption}


\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\volumeyear{2019}

\journalname{XXXXXX}
\articletype{Research Article/Editorial}
\setcounter{page}{01}
 \def\volumeyear{XXXX}
 \def\volumenumber{XX}
  \def\issuemonth{XX-XX}
  \def\issuenumber{X}
  \def\articleid{XX}
  \def\copyrightholder{Andrew Meyer\textit{ et al.}, licensed to ICST}
  \copyrightnote{This is an open access article distributed under the terms of the Creative Commons Attribution license (\url{http://creativecommons.org/licenses/by/3.0/}), which permits unlimited use, distribution and reproduction in any medium so long as the original work is properly cited.}
  \def\articledoi{10.4108/XX.X.X.XX}
\received{XXXX}
  \accepted{XXXX}
  \published{XXXX}

\begin{document}

\runningheads{A. Meyer, S. Roy}{Do Metadata-based Deleted-File-Recovery (DFR) Tools Meet NIST Guidelines?}

\title{Do Metadata-based Deleted-File-Recovery (DFR) Tools Meet NIST Guidelines?}

\author{Andrew Meyer\affil{1}, Sankardas Roy\affil{2}\fnoteref{1}}

\address{\affilnum{1}Computer Science Department, Bowling Green State University, Bowling Green, Ohio, USA\\
\affilnum{2}Computer Science Department, Bowling Green State University, Bowling Green, Ohio, USA}

\abstract{Digital forensics (DF) tools are used for post-mortem investigation of cyber-crimes. 
CFTT (Computer Forensics Tool Testing) Program at National Institute of Standards and Technology (NIST) 
has defined expectations for a DF tool's behavior. Understanding these expectations and how DF tools work 
is critical for ensuring integrity of the forensic analysis results. 
In this paper, we consider standardization of one class of DF tools which are for Deleted File Recovery (DFR). 
We design a list of canonical test file system images to evaluate a DFR tool.
Via extensive experiments we find that many popular DFR tools do not satisfy some of the standards, and 
we compile a comparative analysis of these tools, which could help the user choose the right tool. 
Furthermore, one of our research questions identifies the factors which make a DFR tool fail. 
Moreover, we also provide critique on applicability of the standards. 
Our findings is likely to trigger more research on compliance of standards from the researcher community as well as the practitioners.}

\keywords{Deleted File Recovery, Digital Forensics, Metadata, NIST Guidelines, File System, FAT, NTFS}

\fnotetext[1]{Corresponding author.  Email: \email{sanroy@bgsu.edu}}

\maketitle

\input{intro.tex}
\input{rq.tex}
\input{background.tex}
\input{approach.tex}
\input{discussion.tex}
\input{conclusion.tex}

\ack A. Meyer's work has been partially supported by a grant from BGSU's Center for Undergraduate Research and Scholarship 
(CURS) in summer of 2019. S. Roy's work has been partially supported by a NIST grant (grant number: 70NANB17H321; Year 2017-19) that he has been awarded with as a Co-PI. 
Any opinions or findings expressed in this paper are those of the authors and do not necessarily reflect the views of the funding agencies.
Quinton Currier at BGSU assisted with the testing process.

\bibliographystyle{icstnum}
\bibliography{mybib}

\end{document}
